%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{amsmath}

\begin{document}
\title{The Lunar Mission Launch Simulator Initial Writeup}
\author{Lou Rosas}
\maketitle

\section{History}
Launching Simulators pose a unique challenge in implementation of
physics and real-time monitoring of:
\begin{enumerate}
\item Current Speed
\item Current Altitude
\item Current Drag Coefficient
\item Current Position relative to Earth
\item Current Fuel Content
\item Current Stage
\begin{enumerate}
\item When Staging should occur
\end{enumerate}
\item Current End of Lauch Sequence
\begin{enumerate}
\item When the Capsule is in stable orbit?
\item When all of the Stages are completely finished?
\item When the Capsule is actually in space?
\end{enumerate}
\end{enumerate}
All of these pose particular issues as related to accurately
simulating a launch.

\section{Abstract}
Part of the entire Mission Simulation is the Launch.  The Launch is a
sequence computer simulated.  Modeling the launch sequence is
symbiotic to an actual launch of a rocket sent on an actual space
mission.

\section{Concept}
To gain understanding in all aspects of development of a Mission
Launch Simulator.\\
Including:
\begin{enumerate}
\item Physics
\item Software Development Life Cycle
   \begin{enumerate}
      \item Analysis
      \item Design
      \item Development
      \item Deployment
      \item Continuous Development
      \item Iterative Development
   \end{enumerate}
\item Software Concurrency
   \begin{enumerate}
      \item Mainly centered around the multple software modeling
      objects aggregate to the simulator
   \end{enumerate}
\end{enumerate}

\section{Intent}
Develop the Launch Simulator as part of the Lunar Mission Simulator.

\section{Stakeholders \& Interests}
Anyone interested in using the Launch Simulator.
\begin{itemize}
   \item Space Crews--who want to monitor the launch
   \item Mission Planners--who want a successful Launch Simulator
   \item Engineers/Technicians--who want to view/assess the launch in
   real-time as part of the overall Mission.
\end{itemize}

\section{Typical Success Scenario}
The capsule(s)/payload successfully delivered into space.  A
successful launch is considered:
\begin{enumerate}
   \item Successful ignition of the Launch Vehicle
   \item Successful and complete staging of all the stages of the 
      Launch Vehicle
   \item Obtaining the correct Orbital Altitude
   \item Obtaining the correct Orbital Trajectory
   \item Obtaining the correct Orbital Velocity
   \item Successful separation of the last stage of the Launch Vehicle
      from the capsule(s)/payload
\end{enumerate}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
