%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case 1:  Monitor Pre-Launch}\\
\textbf{Scenario:  }Monitor Delivery System--Monitor Stage\\
\textbf{Scope:  }LaunchSimulator\\
\textbf{Level:  }Flight Controller Goal\\
\textbf{Primary Actor:  }Flight Controller\\
\textbf{Related Use Cases:  }None\\
\textbf{Stakeholders \& Interrests:}
\begin{itemize}
\item Flight Controller:  Wants to monitor the entire stage data during
Pre-Launch for Pre-Launch validity (continue, hold or abort Pre-Launch)
\item Engineer/Technicians:  Wants to monitor the stage data during
Pre-Launch to aprise the Flight Controller to the condition of the
Stage
\item Astronaut:  Wants to monitor the stage data during pre-launch
for mission integrity
\end{itemize}
\textbf{Pre-Conditions:  }The Countdown has started, in Pre-Launch\\\\
\textbf{Post-Conditions:  }The Countdown at 0, the System transitioned
to Initiate Launch\\\\
\textbf{Main Success Scenario:}\\
\begin{tabular}{|p{5.75cm}|p{5.75cm}|}\hline
\textbf{Flight Controller} & \textbf{System}\\\hline
& 1.  Monitors the Pre-Launch Engine Data\\\hline
& 2.  Returns the Pre-Launch Engine Data\\\hline
& 3.  Repeats 1,2 for each Engine\\\hline
& 4.  Monitors the Fuel System Data\\\hline
& 5.  Returns the Fuel System Data\\\hline
& 6.  Repeats 4,5 for each component in the Fuel System\\\hline
& 7.  Reports Countdown at 0\\\hline
8.  Initiate Launch & \\\hline
& 9.  Transitions to Initiate Launch\\\hline
\end{tabular}\\\\
\textbf{Alternative Flows:}
\begin{itemize}
\item[2a.]During the entire Countdown, if the any Engine is ignited,
then the System reports the ignition error.  Flight Controller
issues an Abort.
\item[2b.]During the entire Countdown, if any Engine reports a fuel
flow rate beyond ``tollerance", then the System reports an Engine
error.  Flight Controller issues an Abort.
\item[5a.]During the entire Countdown, if the Stage's Fuel Tanks
report an empty rate beyond ``tollerance", then the System reports a
Leak Error.  Flight Controller issues an Abort.
\item[5b.]During the entire Countdown, if the Stage's Pumps report a
pump rate beyond ``tollerance", then the System reports an Pump Error.
Flight Controller determines next course of action.
\item[5c.]During the entire Countdown, if the Stage's Pumps report a
flow rate beyond ``tollerance", then the System reports at Pump Leak.
Flight controller issues and Abort.
\item[5d.]During the entire Countdown, if the Stage's Fuel Tanks
 report a High Temperature, the the System report the High Temperature
 error.  Flight Controller issues an Abort.
\item[5e.]During the entire Countdown, if the Pipes report a Flow Rate
 beyond ``tollerance", then the System reports a Leak.  Flight
 controller issues and Abort.
\end{itemize}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
