%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case 2:  Iniate Launch/Monitor Launch}\\
\textbf{Scope:  }Launch Simulator\\
\textbf{Level:  }Flight Controller Goal, Astronaut Goal\\
\textbf{Primary Actor:  }Flight Controller\\
\textbf{Secondary Actor:  }Engineer/Technician\\
\textbf{Related Use Cases:  }\textit{Use Case 1:  The Users shall
monitor Pre-Launch Activities}\\
\textbf{Stakeholders \& Interrests:  }
\begin{itemize}
\item Flight Controller:  wants
\begin{itemize}
\item to Initiate Launch
\item to  Monitor Launch Data for launch safety
\begin{itemize}
\item Determine if a Launch Abort is needed
\end{itemize}
\item a Successful Lanch
\end{itemize}
\item Astronaut:  wants
\begin{itemize}
\item a Successful Launch
\item to Monitor Launch data for launch safety
\begin{itemize}
\item Determine if a Launch abort is needed
\end{itemize}
\end{itemize}
\item Engineer/Technician:  Wants to monitor launch data of their
responsibility for launch integrity assessment:  to advise the Flight
Controller
\item Administrator:  wants a successful Launch
\item Local and Federal Politicians:  want
\begin{itemize}
\item a successful Launch for
campaign, re-election and other political purposes
\item a successful Launch for policy assesment for program funding and
continuation
\item technical success for local and national pride
\end{itemize}
\end{itemize}
\textbf{Pre-Conditions:  }All Pre-Launch Activities are complete:  the
Countdown is at Zero, there is no hold nor abort on the Countdown, the
System indicates no errors in the Pre-Launch Data\\
\textbf{Post-Conditions:  }The Trasistion out of Launch successful\\\\
\textbf{Main Success Scenario:  }\\
\begin{tabular}{|p{5.75cm}|p{5.75cm}|}\hline
\textbf{Flight Controller} & \textbf{System}\\\hline
&1.  Indicates Countdown at zero and ready to launch\\\hline
2. Intiates Lauch & \\\hline
& 3.  Directs Engines to ignite\\\hline
& 4.  Returns confirmation of the engine ignition\\\hline
& 5.  Monitors Engine Thrust Data\\\hline
& 6.  Returns Engine Trust Data\\\hline
& 7.  Repeats 5 \& 6 until Engine Trust adequate to lift
rocket\\\hline
& 8.  Rocket ready to Launch\\\hline
9. Launch Rocket &\\\hline
& 9.   Execute the Launching Mechanism (Launches Rocket)\\\hline
& 10.  Monitors Engine Thrust Data\\\hline
& 11.  Returns Engine Thrust Data\\\hline
& 12.  Monitors Rocket for Clearing the Launch Tower\\\hline
& 13.  Returns Rocket's current height\\\hline
& 14.  Repeats steps 10 through 13 until Rocket Clears Launch
Tower\\\hline
& 13.  Returns Rocket Cleared Tower\\\hline
& 14.  Transitions to Launch upon Rocket Clearing the Launch
Tower\\\hline
& 15.  Informs of Transition\\\hline 
& 16.  Starts the Flight Time Clock\\\hline
& 17.  Periodically returns the Flight Time to the actors
throughout the durration of the launch\\\hline
& 18. Periodically monitors/returns launch data to the actors
throughout the durration of the launch\\\hline
& 19.  Performs Final Stage Separation from the payload/capsule\\\hline
& 20.  Informs actors of Final Stage Separation\\\hline
& 21. Transitions out of Launch (Launch is complete)\\\hline
& 22. Alerts the Actors of the Transition\\\hline
\end{tabular}\\\\
\textbf{Alternative Flows:}
\begin{itemize}
\item[4a.]If the Engines do not ignite, then the System Alerts the
Flight Controller of the issue, the Flight Controller aborts the
laumch
\item[5a-7a]If, after an expected time for the Engine Thrust to be
adequate enough to lift the Rocket and there is not enough Engine
thrust to lift the Rocket, then the System issues an Engine
Thrust Failure
\item[9a]If the Flight Controller aborts the Launch, the
System will not activate the Launch Mechinism, all the actors are to
follow their respective Launch Abort Procedures.
\item[5b.-7b,10a.11a.] If there is an Engine Thrust Failure, then the
System alerts the Flight Controller of the Engine Thrust Failure. The
Flight Controller aborts the launch.
\item[15a]In the event of a Launch Abort, the System will not
transition to Launch
\item[16a.] In the event of a Flight Time Clock failure, the System
will alert the Actors.  The Flight Controller will initiate manually the
Flight Time Clock and the Flight Time will be kept outside of the
System
\end{itemize}
\textbf{Special Requirements:}
\begin{itemize}
\item The Launch Initialization is from when the Flight Director
Initiates the Launch Sequence to when the Rocket Clears the Launch
Tower.  The Flight Director has the ability to Abort the Lauch
Initialization.  Special Abort Procedures must be developed and
followed by the Flight Controller, and the Astronauts.
\item Several factors and data points are required to determine
if/when the Rocket is ready to Launch.  The System will monitor all
of these factors.  All of these factors must be in a stable and
exprected state before the System will advise on launching the Rocket.
\item There is only one point of Decision for the Abort.  That decision
rests with the Flight Controller.  Currently, the Flight Controller
takes no advisement other than System Data.
\item The Launch Mechanism will not release the delivery system
(rocket) until enough lift thrust is built up.
\end{itemize}
\textbf{Technology \& Variations List}
\begin{itemize}
\item[*] The Launch Initialization data can be viewed simultaneously,
or chose to view selected Launch Initialization data, at the discretion
of the Flight Controller.
\item[*]  If the System is automated, then the System would determine
when to ignite the engines, when  to execute the Launching
Mechanism, and make the decision to abort the Launch Sequence.  The
Flight Director would have final authority.
\item[2a]The Flight Controller can chose not to Initiate the Launch
\end{itemize}
\textbf{Frequency of Occurrence:  }Almost continuoulsy.  Based on the
Frequency of desired Launches.\\\\
\textbf{Open Issues:  }
\begin{itemize}
\item Need to create a list of the Lauch Data to monitor:  needed for
the decision for when to launch the Rocket
\item What are the abort procedures?
\item Consider shutting down the Rocket engines as part of the abort
procedures
\item If the Rocket engines are not capable of shutdown, consider
other possible abort procedures
\item Should the Astronauts have the ability to abort the Launch
initialization?
\item If the Engine thrust is inadequate to lift the to launch and
the Flight Director does not executes the Launch Rocket procedure,
should there be a System Override where the Launching Mechanism is not
executed?
\end{itemize}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
