%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case 1:  Monitor Pre-Launch Activities}\\
\textbf{Scope:  }Launch Simulator\\
\textbf{Level:  }Flight Controller Goal\\
\textbf{Primary Actor:  }Flight Controller\\
\textbf{Secondary Actor:  }Astronaut, Engineer/Technician\\
\textbf{Related Use Cases:  }None\\
\textbf{Stakeholders \& Interrests:  }
\begin{itemize}
\item Flight Controller:  wants to monitor the Pre-Launch Data
\item Flight Controller:  wants to monitor the Countdown Time
\item Flight Controller:  wants to asses the validity of the Countdown
\begin{itemize}
\item Continue the Countdown
\item Hold the Countdown
\item Abort the Countdown
\end{itemize}
\item Engineer/Technician:  wants to montior selected Pre-Launch data
to ensure the System is working properly and advise the Flight
Controller
\item Astronaut:  wants to monitor Countdown Time
\item Astronaut:  wants to monitor Pre-Launch Data for System
awareness
\end{itemize}
\textbf{Pre-Conditions:  }All the parts of the System are ready to
begin the Countdown, the Launch Simulator is running\\
\textbf{Post-Conditions:  }The Countdown is at zero, the System
transitioned from Pre-Launch to Initiate Launch\\\\
\textbf{Main Success Scenario:  }\\
\begin{tabular}{|p{5.75cm}|p{5.75cm}|}\hline
\textbf{Flight Controller} & \textbf{System}\\\hline
1.  Start the Pre-Launch Sequence & \\\hline
& 2. Request Countdown Time Entry\\\hline
3.  Enters the Countdown Time & \\\hline
& 4.  Returns Countdown Time\\\hline
5.  Starts the Countdown  & \\\hline
& 6.  Transitions to Pre-Launch\\\hline
& 7.  Informs the actors of the transition\\\hline
& 8.  Displays Countdown Time to all actors\\\hline
& 9.  Repeats 6 for the entire countdown\\\hline
& 10.  Monitors Pre-Launch Data\\\hline
& 11. Returns Pre-Launch Data to all the actors\\\hline
& 12.  Repeats 7,8 for the entire Countdown\\\hline
& 13.  Alerts actors when Countdown reaches zero\\\hline
14.  Initiate Launch Sequence & \\\hline
& 15.  Transitions out of Pre-Launch into Intiate Launch\\\hline
& 16.  Informs the actors of the transition\\\hline
\end{tabular}\\\\
\textbf{Alternative Flows:  }
\begin{itemize}
\item[*]  At anytime, the Flight Controller can hold the Countdown
if conditions arise that warant that.
\item[*] At anytime, if the Countdown is on hold, the Flight
Controller can resume the Countdown if the State of the System warants
such a transition;  the Countdown continues at the time stopped
\item[*] If the Countdown is on Hold, the Flight Controller can chose
to
abort the Countdown.  The System responds by abandoning the Countdown,
alerting the Actors of the Abort
\item[3c.]If the Flight Controller enters an unacceptatble Countdown
Time, then the System refuses to set the time and instructs the
Flight Controller to enter an acceptable Countdown Time
\item[11c.]  If the System detects an anomaly in the
Pre-Launch Data, then the System alerts the Users of the anomaly for
the Flight Controller to determine if the anomaly warants a hold in
the
Countdown
\item[11d.]  If there is a Countdown hold, and the System continues to
detect an anomaly in the Pre-Launch Data sent to the Users, then the
Flight Controller can chose to abort the Launch, the System indicates
the Aborted Launch
\item[11e.]  If there is a Countdown hold, the Flight Controller will
resume the countdown if
\begin{enumerate}
\item The Anomaly is fixed and there are no other anomalies
\item The Flight Controller determines the Anomaly is not a threat
to the mission integrity
\item The Anomaly is determined to be errant
\end{enumerate}
The System alerts the Users the Countdown hold is lifted
\end{itemize}
\textbf{Special Requirements: }
\begin{itemize}
\item There is only one point of Decision for the Countdown Hold/
Countdown Abort.  That currently rests with the Flight Controller.  The
Engineers/Technicians and Astronaut can advise the Flight Controller,
in addition to the System:  all based on Pre-Launch Data.
\item There must be a Countdown Time of 1 hour entered before the
Countdown can begin.
\end{itemize}
\textbf{Technology \& Variations List: }
\begin{itemize}
\item[*] All actors can chose to view all the Pre-Launch data at once,
or chose to view selected pre-launch data.  This is very useful for the
Engineers/Technicians for monitoring Their individual System
responsibilities
\item[3d-5c.]The Flight Controller can change the Countdown Time as
desired prior to starting the Countdown.  The System changes the
Countdown time, reflects the change to the Filght Controller.  The
Flight Controller Starts the Countdown as typical
\item [6c-14c]If the System is automated, once the Flight Controller 
inputs the Countdown Time, the System could Initiate the Launch, 
hold the Countdown, abort the Countdown.  The Flight Controller would
have final authority.
\item[9f.] If the System is automated at Countdown and the System
detects an anomaly, then the System can hold the Countdown, alerting
the Users;  the Flight Controller can override the hold and resume the
Countdown
\item[12c.] If the System is automated at Countdown, them the System
will initiate the Launch Sequence at the discretion of the Flight
Controller
\end{itemize}
\textbf{Frequency of Occurence:  }  Almost continuously:  based on the
frequency of desired Launches.\\\\
\textbf{Open Issues:  }
\begin{itemize}
\item What about a fully automated System?
\begin{itemize}
\item The Flight Controller would need to maintain ultimate control?
\end{itemize}
\item Can the Countdown be Aborted without the Hold?
\begin{itemize}
\item Currently goes Countdown-Hold-Abort for a Countdown Abort
\end{itemize}
\item What happens if the Countdown Timer fails?
\end{itemize}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
