%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case 2:  Monitor Countdown}\\
\textbf{Scope:  }Launch Simulator\\
\textbf{Level:  }Flight Controller Goal\\
\textbf{Primary Actor:  }Flight Controller\\
\textbf{Secondary Actors:  }Astronaut. Engineer/Technician\\
\textbf{Related Use Cases:  }\textit{Use Case 1:  The Flight Controller
Shall Monitor Pre-Launch Activities}\\
\textbf{Stake Holders \& Interrests:  }
\begin{itemize}
\item Flight Controller:  wants to monitor the Countdown Time
\item Flight Controller:  wants to control the Countdown Time
\begin{itemize}
\item Enter the Countdown Time
\item Start the Countdown Time
\item Hold the Countdown Time
\item Re-Enter the Countdown Time
\end{itemize}
\item Engineer/Technician:  wants to monitor the Countdown Time
\item Astronaut:  wants to monitor the Countdown Time
\end{itemize}
\textbf{Pre-Conditions:  }The System is ready to accept Countdown Time
Entry from the Flight Controller\\
\textbf{Post-Conditions:  }The Countdown Timer has reached zero (see
\textit{Use Case 1:  The Flight Controller shall monitor Pre-Launch
Activities})\\\\
\textbf{Flow of Events:}\\
\begin{tabular}{|p{5.75cm}|p{5.75cm}|}\hline
\textbf{Flight Controller}&\textbf{System}\\\hline
1. Enters the Countdown Time&\\\hline
& 2. Displays the Countdown Time in Coundown Timer\\\hline
3.  Starts the Countdown Timer &\\\hline
& 4. Countdown from entered time to zero\\\hline
& 5. Displays the Current Countdown Time\\\hline
& 6. Countdown Time Zero\\\hline
\end{tabular}\\\\
\textbf{Alternative Flows:}
\begin{itemize}
\item[*.a]At any time, the Flight Controller can abort the Countdown;
System responds with stoping the Countdown and zeroing out the
Countdown Timer
\item[1a.]The Flight Controller can re-enter another Countdown Time
prior to starting the Countdown Timer:  entering the Countdown Time
as many times as desired
\item[2a.]If the Flight Controller enters a Countdown Time too low as
pre-determined for adequate launch safety, then the System does not
set the entered Countdown Time, alerting the Flight Controller of the
error.  The Flight Controller can choose to enter an appropriate
Countdown Time
\item[4a.]If the Flight Controller chooses to hold the Countdown, then
the System stops the Countdown: displaying the stopped Countdown time.
Countdown Time resumes upon Flight Controller restart:  resuming from
the time stopped.
\end{itemize}
\textbf{Special Requirements:}
\begin{itemize}
\item  There is only one point of decision for the Countdown Hold,
Countdown Abort:  The Flight Controller
\end{itemize}
\textbf{Technology \& Variations List:}
\begin{itemize}
\item[4a.] A typical Countdown Timer.
\item[4b.] The Countdown Timer is interchangeable.
\end{itemize}
\textbf{Frequency of Occurence:  }Almost Continuosly:  Based on the
number of desired Launches and the number of desired Countdowns.\\\\
\textbf{Open Issues:}
\begin{itemize}
\item What is considered a ``safe" Countdown Launch Time?
\item Does a ``safe" Countdown Launch Time depend on the type of
launch and type of Delivery Vehicle (Rocket)?
\end{itemize}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
