%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{amsmath}

\begin{document}
\noindent
\textbf{Start the Launch Goal Writeup}\\\\
\textbf{Actor:  }Flight Control Director\\
At the end of Countdown, Flight Controller Starts the Launch.  The
System responds by ingniting the engines.
\begin{enumerate}
\item Flight Controller Starts the Launch
\item System ignites the Engines and reports ingnition
\item System reports back Initial Launch Data (Telemetry)
\item System releases Vehicle once engines are at full power and
reporting consistent thrust
\end{enumerate}
What happens if the System reports an issue with the rockect?\\
The Flight Controller (Flight Control Director) holds the countdown,
with the option to scrub the Launch.  If the Launch is Scrubbed,
another attempt at a Launch is determined (outside the scope of this
Sysetem).  If the Launch is on hold, the Flight Controller resumes the
countdown once the hold issues are fixed.\\\\
Can the Countdown be automated?\\
Yes.  The Flight Controller monitors the Countdown to ensure the
viablilty and safety of the launch.\\\\
Is the Flight Controller able to view all the viable mission data?\\
Yes.  The Flight Controller choses the mission data to focus.  All the
Mission data is available, the Flight Controller choses what mission
data to focus.\\\\
Can the Flight Director view all the Mission Data at once?\\
Yes--all the Mission Data available.\\\\
In addition, the Flight Director can select Mission Data to focus
their attention.\\\\
Can the whole Launch Startup Sequence be automated?\\
Yes:  Including the decision to start.  Up until the ignition, the
Flight Controller ultimately has the authority to abort/delay the
Launch (and thus, Start of Launch) at any point.
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
