%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case LM-1.1.1.1:  Initialize Engine}\\
\textbf{Scope:} Launch Mission\\
\textbf{Primary Actor:} Flight Director\\
\textbf{Related Use Cases:}\textit{Use Case 1.1.1 Initialize Stage}\\
\textbf{Stake Holders \& Interests:}
\begin{itemize}
   \item Flight Director:  Wants to set up the Launch via initializing
      all the Launch Parameters and Subsystems including:
      \begin{itemize}
         \item Every engine
      \end{itemize}
   \item Mission Planner:  Wants the Mission Initialized with the 
      appropriate Mission Parameters loaded
\end{itemize}
\textbf{Pre-Conditions:}  The Mission System is running and ready to
initialize and monitor the appropriate Systems and Sub-Systems\\
\textbf{Post-Conditions:} The engines are initialized with the
appropriate parameters\\\\
\textbf{Flow of Events:}\\
\begin{tabular}{|p{5.75cm}|p{5.75cm}|}\hline
   \textbf{Flight Director}&\textbf{System}\\\hline
   1.   Mission Parameters File&\\\hline
   &2.  Finds the Engine Parameters File Name and Location\\\hline
   &3.  Goes to the Engine Parameters File Location\\\hline
   &4.  Opens the Engine Parameters File\\\hline
   &5.  Reads the Engine Parameter file appropriate for the Engine
   (See \textit{Use Case 1.1.1 Initialize Stage})\\\hline
   &6.  Initializes the Engine Data with the data from the Engine
   Parameter File\\\hline
   &7.  Alerts the Flight Director the Engine is Initialized\\\hline
\end{tabular}\\\\
\textbf{Extensions (or Alternative Flows):}
\begin{itemize}
\item[2a,3a]If the System cannot find the location of the Engine 
   Parameter File, then the System alerts the Flight Director of the
   error:  indicating an illegitimate file path.  The Flight Director
   either chooses another directory path or exits (aborts) the 
   Mission.
\item[4a]If the System cannot open the Engine Parameter File, then
   the System alerts the Flight Director:  indicating unable to open
      the Parameters File.  The Flight Director either chooses another
      Parameters file, or exits (aborts) the Mission.
   \item[5a]If the System cannot read the Engine Parameters File, then
      the System alerts the Flight Director:  indicating unable to 
      read the Parameters File.  The Flight Director either chooses 
      another Parameters file or exits (aborts) the Mission.
\end{itemize}
\textbf{Special Requirements:}
\begin{itemize}
   \item None
\end{itemize}
\textbf{Technology \& Variations List:}
\begin{itemize}
   \item There could be many types of Engine Parameters and subsequent
      files in different formats:  the System will need to account 
      for that.
   \item Regardless of the type of file, the System Data should 
      follow a Standard.
\end{itemize}
\textbf{Frequency of Occurrence:}
\begin{itemize}
   \item Everytime a Mission is planned or simulated
\end{itemize}
\textbf{Open Issues:}
\begin{itemize}
   \item None
\end{itemize}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
