%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case 1:  Initialize Launch}\\
\textbf{Scope:  }Launch Mission\\
\textbf{Primary Actor:  }Flight Director\\
\textbf{Related Use Cases:  }None\\
\textbf{Stake Holders \& Interests:}
\begin{itemize}
   \item Flight Director:  Wants to set up a Launch by Setting all the
      Launch Parameters and Sub-Systems including
      \begin{itemize}
         \item Rocket
         \item Capsule
         \item Launching Platform
         \item Launching Mechanism
      \end{itemize}
   \item Mission Planner:  Wants the Mission Started  with the 
      appropriate Mission Parameters loaded
   \item Engineers/Technicians: Wants to monitor the entire launch to
      ensure success
\end{itemize}
\textbf{Pre-Conditions:  }The Mission System is running and ready to 
monitor all the appropriate Systems and Sub-Systems.\\
\textbf{Post-Conditions:  }The Launching Mission System is Initialized
with the proper Launching Parameters and Monitoring all Launch Systems
and Sub-Systems\\\\
\textbf{Flow of Events:}\\
\begin{tabular}{|p{5.75cm}|p{5.75cm}|}\hline
   \textbf{Flight Director}&\textbf{System}\\\hline
   1.  Enter the Mission Parameters File &\\\hline
   &2.  Opens Mission Parameters File\\\hline
   &3.  Reads the Parameters File\\\hline
   &4.  Initialize the Launch Systems by sending the Mission 
   Parameters File to each Sub-System\\\hline
   &5.  Alerts of the Initialization Status\\\hline
   &6.  Periodically queries each Sub-System's Status or Each
   Sub-System periodically feeds its current Status\\\hline
   &7.  Alerts of the current Status\\\hline
\end{tabular}\\\\
\textbf{Extensions (or Alternative Flows):}
\begin{itemize}
   \item[2a.]If there is an error in opening the Parameters file,
      then the System alerts the Flight Director of the error:
      indicating unable to open the Parameters file.  The Flight 
      Director either chooses another Parameters file or exits 
      (aborts) the Mission.
   \item[3a.]If the System cannot read the Parameters file, then the
      System alerts the Flight Director of the error:  indicating
      unable to read the Parameters file.  The Flight Director either
      chooses another Parameters file or exits (aborts) the Mission.
   \item[4a.] If any of the Sub-Systems are unable to open the 
      Parameters file, the System alerts the Flight Director of the 
      Error: indicating unable to open the file.  The Flight Director
      either chooses another Parameters file or exits (aborts) the
      Mission
   \item[4b.] If any of the Sub-Systems are unable to read the 
      Parameters file, then the System alerts the Flight Director of 
      the Error:  indicating unable to read the file. The Flight 
      Director either chooses another Parameters file or exits 
      (aborts) the Mission.
   \item[6a.,7a.]The System alerts the Stake Holders of any errors.
      The Flight Director determines the Path for the mission. 
\end{itemize}
\textbf{Special Requirements:}
\begin{itemize}
   \item None
\end{itemize}
\textbf{Technology \& Variations List:}
\begin{itemize}
   \item If the System queries the Sub-Systems, error state and data 
      shall be included.
   \item If the Sub-Systems alert, the Sub-Systems either alert in a
      separate error message or the same update message.
\end{itemize}
\textbf{Frequency of Occurrence:}
\begin{itemize}
   \item Every time a planned Mission is exercised or simulated.
\end{itemize}
\textbf{Open Issues:}
\begin{itemize}
   \item During Initialization, how is System Monitoring accomplished?
      \begin{itemize}
         \item Periodic monitoring of the Subsystems
         \item Subsystems periodic alert
         \item Is there the ability to implement both types of
            monitoring?
      \end{itemize}
\end{itemize}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
