%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Initialize Rocket--Casual Format}\\
\textit{Main Success Scenario}\\
\begin{enumerate}
   \item With the System running, the Flight Director enters the
      Mission Parameters File (See 
      \textit{Use Case 1 Initialize Launch})
   \item System Initializes each Rocket Stage (See 
      \textit{Use Case 1.1.1 Initialize Stage})
   \item System Initializes the Payload/Capsule (See 
      \textit{Use Case 1.1.2 Initialize Capsule})
   \item System finds the Rocket Parameters file name and location.
   \item System goes to the Rocket Parameters file location.
   \item System opens the Rocket Parameters file.
   \item System reads the Rocket Parameters file.
   \item System initializes the Rocket Data with the appropriate
      Rocket Data read in from the Rocket Parameters File
   \item System queries \textbf{or} receives Initialization Status
      from each Stage (See 
      \textit{Use Case 1.1.1 Initialize Stage})
   \item System queries \textbf{or} receives Initialization Status 
      from the Payload/Capsule (See 
      \textit{Use Case 1.1.2 Initialize Capsule})
   \item System returns Initialization Data to the Flight Director
\end{enumerate}
\textit{Alternative Scenarios}
\begin{itemize}
   \item[2a]If the System receives an Initialization Error from 
      any of the Rocket Stages, then the System returns the Error to
      the Flight Director (See 
      \textit{Use Case 1.1.1 Initialize Stage})
   \item[3a]If the System receives an Initialization Error from the
      Payload/Capsule, then the System returns the Error to the Flight Director (See Use Case 1.1.2 Initialize Capsule).
   \item[4a,5a]If the System cannot find the location where the Rocket
      Parameters File is located, then the System returns an Error to 
      the Flight Director:  indicating a non-legitimate file path.
   \item[6a]If the System cannot open the Rocket Parameters file, then
      the System returns an Error to the Flight Director indicating 
      unable to open the Rocket Parameters file.
   \item[7a]If the System cannot read the Rocket Parameters File, then
      the System returns an Error to the Flight Director indicating 
      unable to read the Rocket Parameters file.
   \item[9a]If the System receives an Error from any of the Stages,
      then the System returns the Error to the Flight Director (See
      \textit{Use Case 1.1.1 Initialize Stage})
   \item [10a]If the System receives an Error from the Capsule, then
      the System returns the Error to the Flight Director (See 
      \textit{Use Case 1.1.2 Initialize Capsule})
\end{itemize}
\textit{Notes/Constraints}
\begin{itemize}
   \item[11a]The System indirectly alerts the Stake Holders via an
      upward cascade of alerts/queries (See 
      \textit{Use Case 1.1.1 Initialize Stage, 
      Use Case 1.1.2 Initialize Capsule})
\end{itemize}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
