%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case LM-1.1.2:  Initialize Capsule}\\
\textbf{Scope:  }Launch Mission\\
\textbf{Primary Actor: }Flight Director\\
\textbf{Secondary Actors: }None\\
\textbf{Related Use Cases:  }\textit{Use Case 1:  Initialize Launch}\\
\textbf{Stake Holders \& Interests:}
\begin{itemize}
   \item Flight Director:  Wants to set up a Launch via initializing
      all the Launch Parameters, System and Sub-Systems Including:
      \begin{itemize}
         \item Capsule/Payload
      \end{itemize}
   \item Mission Planner:  Wants the Mission Initialized with the 
      appropriate Mission Parameters loaded
\end{itemize}
\textbf{Pre-Conditions:  }The Mission System is running and ready to
initialize and monitor the Capsule/Payload.\\
\textbf{Post-Conditions: }The Capsule is initialized with the 
appropriate parameters.\\\\
\textbf{Flow of Events:}\\
\begin{tabular}{|p{5.75cm}|p{5.75cm}|}\hline
   \textbf{Flight Director}&\textbf{System}\\\hline
 1. Mission Parameters file (See 
    \textit{Use Case 1 Initialize Launch})&\\\hline
&2. Finds the Capsule Parameters File and location\\\hline
&3. Goes to the file path of the Capsule Parameters File\\\hline
&4. Opens the Capsule Parameters File\\\hline
&5. Reads the Capsule Parameters File\\\hline
&6. Initializes the Capsule Data with the appropriate Capsule Data
    read in from the Capsule Parameter File\\\hline
&7. Initialization Status returned to the Flight Director\\\hline
\end{tabular}\\\\
\textbf{Extensions (or Alternative Flows):}
\begin{itemize}
\item[2a,3a]If the System cannot find the location of the Capsule 
Parameters File, then the System returns an Error to the Flight 
Director:  indicating not a legitimate file path.  The Flight Director
determines the next course of action.
\item[4a]If the System cannot open the Capsule Parameters File, then
the System returns an Error to the Flight Director:  indicating unable
to open the Capsule Parameters File.  The Flight Director determines
the next course of action.
\item[5a]If the System cannot read the Capsule Parameters File, then
the System returns an Error to the Flight Director:  indicating unable
to read the Capsule Parameters File.  The Flight Director determines
the next course of action.
\end{itemize}
\textbf{Notes/Constraints:}
\begin{enumerate}
   \item[*a]This Use Case documents the Capsule Initialization, not 
      the Capsule Monitoring (See 
      \textit{Use Case 4.1:  Monitor Initialization}) for Capsule 
      Monitoring
   \item[*b]The next course of action for the Flight Director is
      aborting the mission or choosing another Mission Parameter File
   \item[6a]The System indirectly alerts the Stake Holders via an 
      upward cascade of alerts/queries (See 
      \textit{Use Case 1.1 Initialize Rocket})
\end{enumerate}
\textbf{Special Requirements:}
\begin{itemize}
   \item None
\end{itemize}
\textbf{Technology \& Variations List:}
\begin{itemize}
   \item There could be many types for Mission Parameters Files in 
      different formats for the components.  The System will need to
      account for all the different types of files.
   \item Regardless of file type, the System Data should follow a 
      standard.
\end{itemize}
\textbf{Frequency of Occurrence:}
\begin{itemize}
   \item Everytime a Mission is planned or simulated.
\end{itemize}
\textbf{Open Issues:}
\begin{itemize}
   \item None
\end{itemize}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
