%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case LM-1.1.1.2:  Initialize Fuel System}\\
\textbf{Scope:}  Launch Mission\\
\textbf{Primary Actor:}  Flight Director\\
\textbf{Related Use Cases:  } 
\textit{Use Case 1.1.1.2.1: Initialize Fuel Tank},\\ 
\textit{Use Case 1.1.1.2.2: Initialize Fuel Pump},\\ 
\textit{Use Case 1.1.1.2.3:  Initialize Fuel Pipe}\\
\textbf{Stake Holders \& Interests:}
\begin{itemize}
   \item Flight Director:  Wants to set up a Launch via setting all
      the Launch Parameters and Sub-Systems including:
   \begin{itemize}
      \item Rocket and Fuel System
   \end{itemize}
   \item Mission Planner:  Wants the Mission Initialized with the
      appropriate Mission Parameters loaded
\end{itemize}
\textbf{Pre-Conditions:  }The Mission System is running and ready to
initialize and monitor the appropriate Systems and Sub-Systems.\\
\textbf{Post-Conditions: }The Fuel System is initialized with the
appropriate parameters.\\\\
\textbf{Flow of Events:}\\
\begin{tabular}{|p{5.75cm}|p{5.75cm}|}\hline
   \textbf{Flight Director}&\textbf{System}\\\hline
   1. Enters the Mission Parameters File&\\\hline
   &2. Initialize each Fuel Tank (See 
   \textit{Use Case 1.1.1.2.1:  Initialize Fuel Tank})\\\hline
   &3. Initialize each Fuel Pump (See 
   \textit{Use Case 1.1.1.2.2:  Initialize Fuel Pump})\\\hline
   &4. Initialize each Fuel Pipe (See 
   \textit{Use Case 1.1.1.2.3:  Initialize Fuel Pipe})\\\hline
   5. Initialization Fuel System Status&\\\hline
\end{tabular}\\\\
\textbf{Extensions (or Alternative Flows):}
\begin{itemize}
   \item[2a]If the System receives an Initialization Error from any
      of the Fuel Tanks, then the System returns the Error to the 
      Flight Director.  The Flight Director determines to continue or
      exit (abort) the Mission.
   \item[3a]If the System receives an Initialization Error from any 
      of the Fuel Pumps, then the System returns the Error to the 
      Flight Director.  The Flight Director determines to continue or
      exit (abort) the Mission.
   \item[4a]If the System receives an Initialization Error from any 
      of the Fuel Pipes, then the System returns the Error to the 
      Flight Director.  The Flight Director determines to continue 
      or exit (abort) the Mission.
\end{itemize}
\textbf{Notes/Constraints:}
\begin{itemize}
   \item[*a]This Use Case documents the Fuel System Initialization,
      not the Monitoring of the Fuel System (See 
      \textit{Use Case 4.1:  Monitor Initialization} for System 
      Monitoring
   \item[5a]The System indirectly alerts the Stake Holders via an
      upward cascade of alerts/queries with the Current Stage (See 
      \textit{Use Case 1.1.1:  Initialize Stage})
\end{itemize}
\textbf{Special Requirements:}
\begin{itemize}
   \item None
\end{itemize}
\textbf{Technology  \& Variations List:}
\begin{itemize}
   \item There could be many types of Mission Parameter Files in
      different formats for the Pipes, Tanks and Pumps:  the System 
      will need to possibly account for all of the different types of
      files.
   \item Regardless of the type of file, the System Data should
      follow a standard.
\end{itemize}
\textbf{Frequency of Occurrence:}
\begin{itemize}
   \item Every time a Mission is planned or simulated.
\end{itemize}
\textbf{Open Issues:}
\begin{itemize}
   \item None
\end{itemize}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
