%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case LM-1.1.1:  Initialize Stage}\\
\textbf{Scope: }Launch Mission\\
\textbf{Primary Actor: }Flight Director\\
\textbf{Related Use Cases:  }\textit{Use Case 1: Initialize Launch},\\
\textit{Use Case 1.1.1.1:  Initialize Engine},\\
\textit{Use Case 1.1.1.2:  Initialize Fuel System}\\
\textbf{Stake Holders  \& Interests:}
\begin{itemize}
   \item Flight Director:  Wants to set up a Launch via initializing
      all the Launch Parameters, Systems and Sub-Systems including:
      \begin{itemize}
         \item Rocket and Fuel System
      \end{itemize}
   \item Mission Planner: Wants the Mission Initialized with the 
      appropriate Mission Parameters loaded
\end{itemize}
\textbf{Pre-Conditions:  }The Mission System is running and ready to
initialize and monitor the appropriate Systems and Sub-Systems\\
\textbf{Post-Conditions: }The Stage is Initialized with the 
appropriate parameters:  including everything that composes a 
Stage\\\\
\textbf{Flow of Events:}\\
\begin{tabular}{|p{5.75cm}|p{5.75cm}|}\hline
   \textbf{Flight Director}&\textbf{System}\\\hline
   1.  Enters the Mission Parameters File (See 
   \textit{Use Case 1:Initialize Launch})&\\\hline
   &2. Initializes each Engine in the Stage (See 
   \textit{Use Case 1.1.1.1: Initialize Engine})\\\hline
   &3. Initializes the Fuel System in the Stage (See 
   \textit{Use Case 1.1.1.2: Initialize Fuel System})\\\hline	
   &4. Finds the Stage Parameters File and location\\\hline
   &5. Goes to the Stage Parameters File location\\\hline
   &6. Opens the Stage Parameters file\\\hline
   &7. Reads the Stage Parameters file\\\hline
   &8. Initializes the Stage Data with the appropriate Stage data 
   read in from the Stage Parameters File\\\hline
   &9. Initialization Status returned to the Flight Director\\\hline
\end{tabular}\\\\
\textbf{Extensions (or Alternative Flows):}
\begin{itemize}
\item[2a]If the System receives an initialization error from the 
   Engines, then the System returns the Error to the Flight Director 
   (See \textit{Use Case 1.1.1.1 Initialize Engine)}.  The Flight 
   Director determines the next course of action.
\item[3a]If the System receives an initialization error from the Fuel
   System, then the System returns the Error to the Flight Director
   (See \textit{Use Case 1.1.1.2 Initialize Fuel System}).  The Flight
   Director determines the next course of action.
\item[4a,5a]If the System cannot find the location where the Stage 
   Parameters File is located, then the System returns the Error to 
   the Flight Director:  indicating an non-legitimate file path. The 
   Flight Director determines the next course of action.
\item[6a]If the System cannot open the Stage Parameters File, then
   the System returns the error to the Flight Director:  indicating
   unable to open the Stage Parameters file.  The Flight Director 
   determines the next course of action.
\item[7a]If the System cannot read the Stage Parameters File, then the
   System returns an Error to the Flight Director:  indicating unable
   to read the Stage Parameters file.  The Flight Director determines
   the next course of action.
\end{itemize}
\textbf{Notes/Constraints:}
\begin{itemize}
   \item[*a]This Use Case documents the Stage Initialization, not the 
      Stage Monitoring (See 
      \textit{Use Case 4.1: Monitor Initialization}) for Stage 
      Monitoring
   \item[*b]The Next Course of Action for the Flight Director is 
      aborting the mission or chosing another Mission Parameters File
   \item[9a]The System indirectly alerts the Stake Holders via an 
      upward cascade of alerts/queries with the Rocket (See 
      \textit{Use Case 1.1:  Initialize Rocket})
\end{itemize}
\textbf{Special Requirements:}
\begin{itemize}
   \item None
\end{itemize}
\textbf{Technology \& Variations List:}
\begin{itemize}
   \item There could be many types of Mission Parameters Files in 
      different formats for the components, the System will possibly 
      need to account for all the different types of files.
   \item Regardless of the type fo file, the System Data should 
      follow a Standard
\end{itemize}
\textbf{Frequency of Occurrence:}
\begin{itemize}
   \item Every time a Mission is planned or simulated.
\end{itemize}
\textbf{Open Issues:}
\begin{itemize}
   \item None
\end{itemize}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
