%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case LM--1.1: Initialize Rocket}\\
\textbf{Scope: }Launch Mission\\
\textbf{Primary Actor: }Flight Director\\
\textbf{Secondary Actor:} None\\
\textbf{Related Use Cases: }\textit{Use Case 1 Initialize Launch},\\
\textit{Use Case 1.1.1 Initialize Stage},\\
\textit{Use Case 1.1.2 Initialize Capsule}\\
\textbf{Stake Holders \& Interests:}
\begin{itemize}
   \item Flight Director:  Wants to set up a Launch via initializing
      all the Launch Parameters, Systems, Sub-Systems including:
      \begin{itemize}
         \item Rocket
      \end{itemize}
   \item Mission Planner:  Wants the Mission Initialized with the
      appropriate Mission Parameters loaded
\end{itemize}
\textbf{Pre-Conditions:  }The System is running and ready to
initialize and monitor the appropriate Systems and Sub-Systems\\
\textbf{Post-Conditions:  }The Rocket and all the components is
initialized with the appropriate parameters\\\\
\textbf{Flow of Events:}\\
\begin{tabular}{|p{5.75cm}|p{5.75cm}|}\hline
   \textbf{Flight Director}&\textbf{System}\\\hline
   1.  Enters the Mission Parameters File (See 
   \textit{Use Case 1 Initialize Launch})&\\\hline
   &2. Initialize each Stage (See 
   \textit{Use Case 1.1.1 Initialize Stage})\\\hline
   &3. Initialize the Payload/Capsule (See 
   \textit{Use Case 1.1.2 Initialize Capsule})\\\hline
   &4. Finds the Rocket Parameters file name and location\\\hline
   &5. Goes to the Rocket Parameters file location\\\hline
   &6. Opens the Rocket Parameters file\\\hline
   &7. Reads the Rocket Parameters file\\\hline
   &8. Initializes the Rocket Data with the appropriate Rocket Data
   read in from the Rocket Parameters file\\\hline
   &9. Queries \textbf{or} receives Initialization Status from each
   Stage (See \textit{Use Case 1.1.1 Initialize Stage})\\\hline
   &10. Queries \textbf{or} receives Initialization Status from the
   Payload/Capsule (See 
   \textit{Use Case 1.1.2 Initialize Capsule})\\\hline
   11. Receives Initialization Data&\\\hline
\end{tabular}\\\\
\textbf{Extensions (or Alternative Flows):}
\begin{itemize}
    \item[2a]If the System receives an Initialization Error from any
       of the Stages, then the System returns the Error to the Flight
       Director (See 
       \textit{Use Case 1.1.1 Initialize Stage}).  The Flight Director
       determines the next course of action.
    \item[3a]If the System receives an Initialization Error from the
       Payload/Capsule, then the System returns the Error to the 
       Flight Director (See 
       \textit{Use Case 1.1.2 Initialize Capsule}).  The Flight 
       Director determines the next course of action.
    \item[4a,5a]If the System cannot find the location where the
       Rocket Parameters File is located, then the System returns an
       Error to the Flight Director indicating a non-legitimate file
       path.  The Flight Director determines the next course of 
       action.
    \item[6a]If the System cannot open the Rocket Parameters file,
       then the System returns an Error to the Flight Director
       indicating unable to open the Rocket Parameters file.  The
       Flight Director determines the next course of action.
    \item[7a]If the System cannot read the Rocket Parameters file,
       then the System returns an Error to the Flight Director
       indicating unable to read the Rocket Parameters file.  The
       Flight Director determines the next course of action.
    \item[9a]If the System receives an Error from any of the Stages,
       then the System returns the Error to the Flight Director (See
       \textit{Use Case 1.1.1 Initialize Stage}).  The Flight Director
       determines the next course of action.
    \item[10a]If the System receives an Error from the Capsule, then
       the System returns the Error to the Flight Director (See
       \textit{Use Case 1.1.2 Initialize Capsule}).  The Flight
       Director determines the next course of action.
\end{itemize}
\textbf{Notes/Constraints:}
\begin{itemize}
   \item[*a]This Use Case documents the Rocket Initialization, not
      the Rocket Monitoring (See 
      \textit{Use Case 4.1 Monitor Initialization})
   \item[*b]The Next Course of action for the Flight Director is 
      aborting the mission or choosing another Mission Parameters 
      File.
   \item[11a]The System indirectly alerts the Stake Holders via an
      upward cascade of alerts/queries (See 
      \textit{Use Case 1.1.1 Initialize Stage,
      Use Case 1.1.2 Initialize Capsule})
\end{itemize}
\textbf{Special Requirements:}
\begin{itemize}
   \item None
\end{itemize}
\textbf{Technology \& Variations List:}
\begin{itemize}
   \item There could be many types of Mission Parameters Files in
      different formats for the System Composition.  The System needs
      to account for all the different types of files and read them
      accordingly.
   \item Regardless of the type of file, the System Data should follow
      a standard
\end{itemize}
\textbf{Frequency of Occurrence:}
\begin{itemize}
   \item Every time a Mission is planned or simulated
\end{itemize}
\textbf{Open Issues:}
\begin{itemize}
   \item None
\end{itemize}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
