%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case UC-1.1.1.2.3:  Initialize Fuel Pipe}\\
\textbf{Scope:}  Launch Mission\\
\textbf{Primary Actor:} Flight Director\\
\textbf{Related Use Cases:} 
\textit{Use Case 1.1.1.2 Initialize Fuel System}\\
\textbf{Stake Holders  \& Interests:}
\begin{itemize}
   \item Flight Director:  Wants to set up a Launch via setting all
      the Launch Parameters and Sub-Systems including:
      \begin{itemize}
         \item Rocket and the Fuel System
      \end{itemize}
   \item Mission Planner:  Wants the Mission Initialized with the
      appropriate Mission Parameters loaded
\end{itemize}
\textbf{Pre-Conditions:  }The Mission System is running and ready to
initialize and monitor the appropriate Systems and Sub-Systems\\
\textbf{Post-Conditions:  }The Fuel Pipe is Initialized with the
appropriate parameters\\\\
\textbf{Flow of Events:}\\
\begin{tabular}{|p{5.75cm}|p{5.75cm}|}\hline
   \textbf{Flight Director}&\textbf{System}\\\hline
   1.  Enter the Mission Parameter File &\\\hline
   &2.  Finds the Pipe Parameter File name and location\\\hline
   &3.  Goes to the Pipe Parameter File Location\\\hline
   &4.  Opens the Pipe Parameter File\\\hline
   &5.  Reads the Parameter Data appropriate for the Pipe (See 
   \textit{Use Case 1.1.1.2 Initialize Fuel System})\\\hline
   &6.  Initializes the Pipe Data with the data from the Pipe 
   Parameter File\\\hline
   &7.   Alerts the Flight Director the Pipe is initialized\\\hline
\end{tabular}\\\\
\textbf{Extensions (or Alternative Flows):}
\begin{itemize}
   \item[2a,3a]If the System cannot find the location of the Pipe
      Parameter File, then the System alerts the Flight Director of 
      the error:  indicating not a legitimate file path.  The Flight 
      Director either chooses another directory path or exits 
      (aborts) the Mission.
   \item[4a]If the System cannot open the Pipe Parameter file, then 
      the System alerts the Flight Director of the Error:  indicating
      unable to open the Parameters File.  The Flight Director either
      chooses another Parameters file, or exits (aborts) the Mission.
   \item[5a]If the System cannot read the Pipe Parameter File, then
      the System alerts the Flight Director of the Error:  indicating
      unable to read the Parameters File.  The Flight director either
      chooses another Parameters file or exits (aborts) the Mission.
\end{itemize}
\textbf{Special Requirements:}
\begin{itemize}
   \item None
\end{itemize}
\textbf{Technology \& Variations List:}
\begin{itemize}
   \item There could be many types of Pipe Parameter Files in
      different formats, the System will need to possibly account for
      that.
   \item Regardless of the type of file, the System Data should follow
      a Standard.
\end{itemize}
\textbf{Frequency of Occurrence:}
\begin{itemize}
   \item Every Time a Mission planned or simulated.
\end{itemize}
\textbf{Open Issues:}
\begin{itemize}
   \item None
\end{itemize}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
